Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-01 hazelnut-popl17.tex
adding a little more meat to the action macros future work paragraph, closing #11
Adding acks
adding that sweet sweet AEC badge

@@

\subsubsection{Programmable Actions}
Our language of actions is intentionally primitive. However, even now it
acts much like a simple imperative command language. This suggests future
expansion to, for example, a true tactic language. Alternatively, it may be
more useful to develop the notion of an \emph{action macro}, whereby
functional programs could themselves be lifted to the level of actions to
compute non-trivial compound actions.

@@

>>>>

\usepackage[firstpage]{draftwatermark}
\SetWatermarkText{\hspace*{8in}\raisebox{6.5in}{\includegraphics[scale=0.1]{aec-badge-popl}}}
\SetWatermarkAngle{0}

@@

\subsubsection{Programmable Actions}
Our language of actions is intentionally primitive. However, even now it
acts much like a simple imperative command language. This suggests future
expansion to, for example, a true tactic language. Alternatively, it may be
more useful to develop the notion of an \emph{action macro}, whereby
functional programs could themselves be lifted to the level of actions to
compute non-trivial compound actions. Such compound actions would give a
uniform description of transformations ranging from the simple -- like
``move the cursor to the next hole to the right'' -- to quite complex whole
program refactoring, while remaining subject to the core Hazelnut
metatheory.

@@

\acks
\input{acks.tex}
